---
title: "Journal (reproducible report)"
author: "Manuel Strübing"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Challenge 1 - Sales Analysis

Last compiled: `r Sys.Date()`

```{r Challenge 1 - Sales Analysis, fig.width = 13, fig.height = 7}

# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
library(lubridate)

# 2.0 Importing Files ----
bikes_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/bikes.xlsx")
bikeshops_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# 5.0 Wrangling Data

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%

    # 5.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Reorganize
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))


####### Challenge

##### Sales by State - Manipulate

sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  separate(col = location,
           into = c('city', 'state'),
           sep = ', ',
           convert = T) %>%
  
  select(state, total_price) %>%
  
  group_by(state)  %>%
  
  summarize(sales = sum(total_price)) %>%
  
  arrange(state) %>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

#### Sales by State and Year - Manipulate

sales_by_state_and_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  separate(col = location,
           into = c('city', 'state'),
           sep = ', ',
           convert = T) %>%
  
  mutate(year = year(order_date)) %>%
  
  select(state, year, total_price) %>%
  
  group_by(state, year)  %>%

  summarize(sales = sum(total_price)) %>%
  
  arrange(state, year) %>%
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))


for (jj in c(1:nrow(sales_by_state_tbl))) {

  assign(
    paste("sales_in_", 
          sales_by_state_tbl[jj,1], 
          sep = ''),
    sales_by_state_and_year_tbl[sales_by_state_and_year_tbl$state == sales_by_state_tbl[[jj,1]],]
        )
}


plotti <- function(loc_data, loc_city) {
  
    eval(as.name(loc_data)) %>%

    ggplot(aes(x = year, y = sales)) +

    geom_col(fill = "#008E19") +

    theme_minimal(base_size = 15) +

    geom_label(aes(label = sales_text)) +
    
    geom_smooth(method = "lm", se = FALSE) +

    scale_y_continuous(labels =
              scales::dollar_format(big.mark = ".",
              decimal.mark = ",",
              prefix = "",
              suffix = " €")) +
    
    labs(title = paste("Revenue by year in ",
              loc_city, sep=""),
              x = "Year",
              y = "Revenue")
}

## Sales by State - Visualize

sales_by_state_tbl %>%
  
  arrange(sales) %>%
  
  mutate(state = factor(state, levels = state)) %>%
  
  ggplot(aes(x = state, y = sales)) +

  geom_col(fill = "#008E19") +

  theme_minimal(base_size = 15) +

  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

  geom_label(aes(label = sales_text)) +

  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "State",
    y = "Revenue"
  )

## Sales by State and Year - Visualize
 
plotti(loc_data = "sales_in_Baden-Württemberg",
       loc_city = "Baden-Württemberg")
plotti(loc_data = "sales_in_Bavaria",
       loc_city = "Bavaria")
plotti(loc_data = "sales_in_Berlin",
       loc_city = "Berlin")
plotti(loc_data = "sales_in_Bremen",
       loc_city = "Bremen")
plotti(loc_data = "sales_in_Hamburg",
       loc_city = "Hamburg")
plotti(loc_data = "sales_in_Hesse",
       loc_city = "Hesse")
plotti(loc_data = "sales_in_Lower Saxony",
       loc_city = "Lower Saxony")
plotti(loc_data = "sales_in_Mecklenburg-Western Pomerania",
       loc_city = "Mecklenburg-Western Pomerania")
plotti(loc_data = "sales_in_North Rhine-Westphalia",
       loc_city = "North Rhine-Westphalia")
plotti(loc_data = "sales_in_Saxony",
       loc_city = "Saxony")
plotti(loc_data = "sales_in_Saxony-Anhalt",
       loc_city = "Saxony-Anhalt")
plotti(loc_data = "sales_in_Schleswig-Holstein",
       loc_city = "Schleswig-Holstein")
```

# Challenge 2 - Data Acquisition

Last compiled: `r Sys.Date()`

## Part 1 - API Data
### Rick and Morty Characters

```{r Challenge 2 - Data Acqusition Part 1}

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)

Read_API <-function(nr){
  
ram_api <- GET(glue("https://rickandmortyapi.com/api/character/?page={nr}"))

ram_loop <- ram_api   %>%
  .$content  %>% 
  rawToChar()  %>% 
  fromJSON() %>%
  purrr::pluck("results") %>% as_tibble
}

ram_character <- map(c(1:33),Read_API) %>% 
    bind_rows

ram_origin <- bind_cols(ram_character$origin) %>% select(name) %>% rename(origin = name)

ram_location <- bind_cols(ram_character$location) %>% select (name) %>% rename(current_location = name)
    
ram_character <- ram_character %>%
  select(name, status, species, gender) %>% 
  add_column(ram_origin, ram_location) %>%
  arrange(species, status, origin, current_location)

```

## Part 2 - Web Scraping 
### Rosé Bikes

```{r Challenge 2 - Data Acqusition Part 2}


library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(httr)

url <- "https://www.rosebikes.com/bikes"

html <- read_html(url)

bike_tbl <- html %>% 
          html_nodes(".catalog-navigation__link") %>% 
          html_attrs() %>% 
          bind_rows()  %>%
          select(title, href) %>%
  rename(family_url = href, bike_family = title) %>%
  mutate(family_url = glue("https://www.rosebikes.com{family_url}")) %>%
  filter(bike_family != "Sale")

read_categories <- function(nr){
  
  bike_category_url <- bike_tbl$family_url[nr]
  
  bike_category_html <- read_html(bike_category_url)
  
  bike_category_names_tbl <- bike_category_html %>%
    html_nodes(".catalog-category-bikes__title-text") %>%
    html_text() %>%
    stringr::str_extract("(?<=\\n).*(?=\\n)") %>%
    as_tibble 
  
  bike_category_price_tbl <- bike_category_html %>%
    html_nodes(".catalog-category-bikes__price-title") %>%
    html_text() %>%
    stringr::str_extract("(?<=from ).*(?=.00)") %>%
    stringr::str_replace(pattern = ",", replacement = "") %>%
    as_tibble 
  
  pricelist_map <- bind_cols(bike_tbl$bike_family[nr], bike_category_names_tbl, bike_category_price_tbl)
}

pricelist_tbl <- map(c(1:9),read_categories) %>%
  bind_rows() %>% rename(Family = ...1, Category = value...2, Price = value...3)

pricelist_tbl[is.na(pricelist_tbl)] <- "Coming Soon"

pricelist_tbl

```



I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.